Classical mechanics as the high-entropy limit \\ of quantum mechanics

### 2025-12-06 Articles/2024-ClassicalLimit/classicalLimitArticle.tex
Change AoP from a project to a program

\section*{Acknowledgements}
This paper is part of the ongoing Assumptions of Physics project~\cite{aop-book}, which aims to identify a handful of physical principles from which the basic laws can be rigorously derived.

% TODO: include funding information
\paragraph{Funding information}
ML acknowledges funding via the FWF-funded QuantERA project QuSiED with project number I 6008-N.

>>>>

\section*{Acknowledgements}
This paper is part of the research program Assumptions of Physics~\cite{aop-book}, which aims to identify a handful of physical principles from which the basic laws can be rigorously derived.

\paragraph{Funding information}
ML acknowledges funding via the FWF-funded QuantERA project QuSiED with project number I 6008-N.
